Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement

### 2020-12-20 vesicle_code/docs/permeableVes/main.tex
cleaned up contractin example

\begin{figure*}[htp]
%  \ifTikz
  \input{figures/stenosisComposite.tikz}
%  \fi
  \caption{\label{fig:stenosisComposite} (a) A semi-permeable vesicle
  passing through a constricted geometry similar to the experimental
  device in~\cite{abk-fai-sto2006}. (b) A semi-permeable vesicle passing
  through a constricted geometry that is over five times longer. (c) The
  excess pressure of an impermeable and semi-permeable vesicle in the
  short geometry in (a). (d) The reduced area of the semi-permeable
  vesicle in the short geometry in (a). (e) The reduced area of the
  semi-permeable vesicle in the long geometry in (b). In parts (c), (d),
  and (e), the horizontal axis is the x-coordinate of the vesicle's
  center of mass.}
\end{figure*}

@@

\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/contractingComposite.tikz}
  \else
  \includegraphics{figures/contractingComposite.pdf}
  \fi
  \caption{\label{fig:contractingComposite} (a) A semi-permeable vesicle
  passing through a contracting geometry similar to the experimental
  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, 
  the vesicle height is initially $10\mu$m, and the maximum background
  flow velocity is $316\mu$m/s. The fluid flux along the red regions is
  into the vesicle, and the fluid flux along the blue regions is out of
  the vesicle.}
\end{figure*}

>>>>

\begin{figure*}[htp]
  \ifTikz
  \input{figures/stenosisComposite.tikz}
  \else
  \includegraphics{figures/stenosisComposite.pdf}
  \fi
  \caption{\label{fig:stenosisComposite} (a) A semi-permeable vesicle
  passing through a constricted geometry similar to the experimental
  device in~\cite{abk-fai-sto2006}. (b) A semi-permeable vesicle passing
  through a constricted geometry that is over five times longer. (c) The
  excess pressure of an impermeable and semi-permeable vesicle in the
  short geometry in (a). (d) The reduced area of the semi-permeable
  vesicle in the short geometry in (a). (e) The reduced area of the
  semi-permeable vesicle in the long geometry in (b). In parts (c), (d),
  and (e), the horizontal axis is the x-coordinate of the vesicle's
  center of mass.}
\end{figure*}

@@

\begin{itemize}
  \item Vesicle velocity in plot (a) varies from 5 to 24 microns/s
  \item Vesicle velocity in plot (b) varies from 5 to 28 microns/s
  \item Vesicle velocity in plot (c) varies from 0.2 to 2 microns/s
  \item Vesicle velocity in plot (d) varies from 5 to 25 microns/s
  \item Vesicle velocity in plot (g) varies from 14 to 95 microns/s (see
    plot (i))
\end{itemize}

\begin{figure*}[htp]
  \centering
%  \ifTikz
  \input{figures/contractingComposite.tikz}
%  \else
%  \includegraphics{figures/contractingComposite.pdf}
%  \fi
  \caption{\label{fig:contractingComposite} A contracting geometry
  similar to the experimental device in~\cite{wu2015critical}. The
  channel width varies from $18\mu$m to $1.8\mu$m, and it repeats every
  $45\mu$m. The fluid flux along the red regions is into the vesicle,
  and the fluid flux along the blue regions is out of the vesicle.
  (a--c) The ability for a semi-permeable vesicle to pass through the
  constriction depends on the semi-permeability rate. (d--f) The ability
  for a semi-permeable vesicle to pass through the constriction depends
  on the flow rate. (g) A semi-permeable vesicle passing through six
  periods of the constricting geometry. (h) The reduced area with the
  marks representing shapes in (g). (i) The vesicle velocity with the
  marks representing shapes in (g).}
\end{figure*}
